---
title: 'DS400: Assignment V - GitHub and the ticketmaster.com API(R)'
author: "Sahra Pfeifer"
date: '2023-01-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
<div class="alert alert-block alert-info">

In this assignment, you will apply what you have learned about APIs and about version control with Git(Hub).
First, you will acquire data about event venues using the API provided by ticketmaster.com. You will then
use the geospatial data to visualize the extracted data on a map. Finally, you will repeat the same steps for a
different country. It is further required that the entire project and its version history is documented in your
personal GitHub repository.
</div>


```{r}
rm(list = ls())

setwd("C:/Users/Sahra/Desktop/M.Sc DS_WiSe1/DSPM/Assignment 5")
```

### Setting up a new GitHub repository
<div class="alert alert-block alert-info">
(1) Register on github.com in case you have not done this already
</div>

<div class="alert alert-block alert-info">
(2) Initialize a new public repository for this assignment on GitHub.
</div>

<div class="alert alert-block alert-info">
(3) For the following exercises of this assignment, follow the standard Git workflow (i.e., pull the latest
version of the project to your local computer, then stage, commit, and push all the modifications that you
make throughout the project). Every logical programming step should be well documented on GitHub
with a meaningful commit message, so that other people (e.g., your course instructor) can follow and
understand the development history. You can do this either using Shell commands or a Git GUI of your choice.
</div>

<div class="alert alert-block alert-info">
(4) In the HTML file that you submit, include the hyperlink to the project repository (e.g., https://github.
com/yourUserName/yourProjectName)
</div>


### Getting to know the API

<div class="alert alert-block alert-info">
(5) Visit the documentation website for the API provided by ticketmaster.com (see here). Familiarize yourself
with the features and functionalities of the Ticketmaster Discovery API. Have a particular look at
rate limits.
</div>

<div class="alert alert-block alert-info">
(6) Whithin the scope of this assignment, you do not have to request your own API key. Instead retrieve
a valid key from the API Explorer. This API key enables you to perform the GET requests needed
throughout this assignment. Even though this API key is not secret per se (it is publicly visible on the
API Explorer website), please comply to the common secrecy practices discussed in the lecture and the
tutorial: Treat the API key as a secret token. Your API key should neither appear in the code that you
are submitting nor in your public GitHub repository.
</div>

```{r}
# access the key from main script using:
source("API_Explorer_Key.R")
```


### Interacting with the API - the basics

<div class="alert alert-block alert-info">
(7) Perform a first GET request, that searches for event venues in Germany (countryCode = "DE"). Extract
the content from the response object and inspect the resulting list. Describe what you can see.
</div>

```{r}
# load relevant packages:
library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
library(dplyr)

```

***
**Perform GET request**
```{r}
response <- GET("https://app.ticketmaster.com/discovery/v2/venues/?",
                query = list(apikey = TM_expl_key,
                             countryCode= "DE",
                             locale = "*")) %>% content()

```
<div class="alert alert-block alert-info">
We can see....
</div>


<div class="alert alert-block alert-info">
(8) Extract the name, the city, the postalCode and address, as well as the url and the longitude
and latitude of the venues to a data frame. This data frame should have the following structure:
</div>

**Extract the seven columns with a Base R approach**
```{r}
library(tidyverse)
list <- lapply(response$`_embedded`$venues, unlist)

# Ensure all list entries have values for the same keys:
keys <- unique(unlist(lapply(list, names)))
keys


# Fill missing key entries with NA:
list <- lapply(list, function(x) x[match(keys, names(x))])                                                                                                

# use rbind to combine into data.frame:
venues_op <- do.call(rbind.data.frame, list)
colnames(venues_op) <- keys

# extract desired columns
cols <-  c("name","postalCode","url","city.name","address.line1",
           "location.longitude","location.latitude") #in desired order, 

venues_op <- venues_op[cols]
#venues_op for "one page"

# rename columns:
library(data.table)
setnames(venues_op, old = c("city.name", "address.line1",
                            "location.longitude", "location.latitude"),
         new = c("city","adress","longitude","latitude"))

# convert to numeric:
colsnum <- c("postalCode","longitude","latitude")

venues_op[colsnum] <- sapply(venues_op[colsnum], as.numeric)

```

***
**Have a look on the data and print first 10 observations**
```{r}
glimpse(venues_op)
print(head(venues_op,10))
```



### Interacting with the API - advanced

<div class="alert alert-block alert-info">
(9) Have a closer look at the list element named page. Did your GET request from exercise (7) return all
event locations in Germany? Obviously not - there are of course much more venues in Germany than
those contained in this list. Your GET request only yielded the first results page containing the first
20 out of several thousands of venues. Check the API documentation under the section Venue Search.
How can you request the venues from the remaining results pages? Iterate over the results pages and
perform GET requests for all venues in Germany. After each iteration, extract the seven variables name,
city, postalCode, address, url, longitude, and latitude. Join the information in one large
data frame. Print the first 10 rows and the shape of the resulting data frame. The resulting data frame
should look something like this (note that the exact number of search results may have changed since
this document has been last modified):
</div>

```{r}
# store number of totalElements in numeric object:
n <- as.numeric(response[["page"]][["totalElements"]])
n

```

**Define a function**
```{r}

# define a function to request the data and return a list of results
worker <- function(page){
  # enforce a rate limit
  Sys.sleep(.2)
  # call the API and get the respective page
  res_venues <- GET("https://app.ticketmaster.com/discovery/v2/venues/?",
                    query = list(apikey = TM_expl_key,
                                 countryCode= "DE",
                                 page = page,
                                 locale = "*")) 
  
  content(res_venues)$`_embedded`
  
}

```

***

**loop function over each page**
```{r}
for (i in seq_along((n %/% 20) + (n %% 20 > 0))){
  list_all <- map_dfr(1:((n %/% 20) + (n %% 20 > 0)), worker)
  # unlist results, map into dataframe
  list_all <- map_dfr(list_all[[i]], unlist)
  # extract desired columns after each iteration
  venues_all <- list_all[cols]
}
```
# beschreiben warum weniger Ergebnisse in df als n = totalElements:

***
**Adjustments of the dataframe**
```{r}
# rename columns:
library(data.table)
setnames(venues_all, old = c("city.name", "address.line1",
                             "location.longitude", "location.latitude"),
         new = c("city","adress","longitude","latitude"))

# convert to numeric:
colsnum <- c("postalCode","longitude","latitude")

venues_all[colsnum] <- sapply(venues_all[colsnum], as.numeric)
# ---> Vgl Assignment 1!

# have a glimpse on the data:
glimpse(venues_all)         

# print first 10 observations:
print(head(venues_all, 10))

```

***

### Visualizing the extracted data

<div class="alert alert-block alert-info">
(10) Below, you can find code that produces a map of Germany. Add points to the map indicating the locations of the event venues across Germany.
</div>
```{r}
ggplot() +
  borders("world", "Germany", colour = "black", fill = "grey90") +
  theme_void() +
  coord_quickmap() +
  geom_point(data = venues_all,
             aes(x=longitude, y=latitude), colour="red",
             fill="red") +
  labs(title = "Event locations across Germany",
       caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic")) 


```

<div class="alert alert-block alert-info">
(11) You will find that some coordinates lie way beyond the German borders and can be assumed to be faulty.
Set coordinate values to NA where the value of longitude is outside the range (5.866, 15.042) or
where the value of latitude is outside the range (47.270, 55.059) (these coordinate ranges have
been derived from the extreme points of Germany as listed on Wikipedia (see here). For extreme points
of other countries, see here).
</div>

```{r}
ggplot() +
  borders("world", "Germany", colour = "black", fill = "grey90") +
  theme_void() +
  coord_quickmap() +
  geom_point(data = venues_all,
             # in plot directly set NA for all values outside long/lat range of Germany
             aes(x=ifelse(longitude %between% c(5.866, 15.042), 
                          longitude, NA), 
                 y=ifelse(latitude %between% c(47.270, 55.059), 
                          latitude, NA)), colour="red",
             fill="red") +
  labs(title = "Event locations across Germany",
       caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic")) 
# don't use all_venues$latitude but just latitude

```

***

### Event locations in other countries

<div class="alert alert-block alert-info">
(12) Repeat exercises (9)–(11) for another European country of your choice. (Hint: Clean code pays off! If
you have coded the exercises efficiently, only very few adaptions need to be made.)
</div>

**Repeat exercises 9-11 for Spain:**

***
**(9) Exercise**
```{r}
# Check content response:
response_ES <- GET("https://app.ticketmaster.com/discovery/v2/venues/?",
                  query = list(apikey = TM_expl_key,
                               countryCode= "ES",
                               locale = "*")) %>% content()

```

**number of all venues in Spain:**
```{r}
n_ES <- as.numeric(response_ES[["page"]][["totalElements"]])
n_ES
```

**set countryCode in function to "ES"**:
```{r}
worker <- function(page){
    # enforce a rate limit
    Sys.sleep(.2)
    # call the API and get the respective page
    res_venues <- GET("https://app.ticketmaster.com/discovery/v2/venues/",
                      query = list(apikey = TM_expl_key,
                                   countryCode= "ES",
                                   page = page,
                                   # for all locations "*"
                                   locale = "*")) 
    
    # return the search items
    content(res_venues)$`_embedded`
    
}
```

***
**Loop function over all pages**
```{r}
for (i in seq_along((n %/% 20) + (n %% 20 > 0))){
  list_ES <- map_dfr(1:((n %/% 20) + (n %% 20 > 0)), worker)
  list_ES <- map_dfr(list_ES[[i]], unlist)
  venues_ES <- list_ES[cols]
  
}

```

**Adjustments**
```{r}
# rename columns:
setnames(venues_ES, old = c("city.name", "address.line1",
                                "location.longitude", "location.latitude"),
         new = c("city","adress","longitude","latitude"))

# convert to numeric:
venues_ES[colsnum] <- sapply(venues_ES[colsnum], as.numeric)


```

***
**Print first 10 observations of venues in Spain**:
```{r}
glimpse(venues_ES)         
print(head(venues_ES,10))
```

***

**(10) Exercise**
**Plot the results**
```{r}
ggplot() +
  borders("world", "Spain", colour = "black", fill = "grey90") +
  theme_void() +
  coord_quickmap() +
  geom_point(data = venues_ES,
             aes(x=longitude, y=latitude), colour="red",
             fill="red") +
  labs(title = "Event locations across Spain",
       caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic")) 
```

***

**(11) Exercise**
```{r}
ggplot() +
  borders("world", "Spain", colour = "black", fill = "grey90") +
  theme_void() +
  coord_quickmap() +
  geom_point(data = venues_ES,
             # in plot directly set NA for all values outside long/lat range of Germany
             aes(x=ifelse(longitude %between% c(-17.934,4.289), 
                          longitude, NA), 
                 y=ifelse(latitude %between% c(27.633, 43.738), 
                          latitude, NA)), colour="red",
             fill="red") +
  labs(title = "Event locations across Spain",
       caption = "Source: ticketmaster.com") +
  theme(title = element_text(size=8, face='bold'),
        plot.caption = element_text(face = "italic")) 
# don't use all_venues$latitude but just latitude


```


